% Do NOT change this "Section" title
% and do NOT add more "Section" level titles.
\section{Conclusion}\label{sec:conclusion}
The sponsorship and marketing is of great importance for the outcome of the project and therefore there should be at least one person working on it. Preferably a whole team. You will realize that time is scarce, so you need to get going as fast as possible. It would actually have been best to start the sponsorship gathering several months prior to the project start.

When searching for sponsors you will find yourself most successful if you use your own contacts to get into contact with the right people and companies. If you contact those persons yourself, then refer to the common contact. An even better way is to get your contacts to write to the person they know at first, giving them a heads up before you contact them.

To be most efficient when talking to sponsors you have to be prepared. This requires some cooperation with the rest of the project members. You have to be on them right from the beginning to acquire a list of parts you need/want. Companies will like to know what they can contribute with and it is more likely that they can give you parts rather than money. They will also like to know your budget, where the project is heading, if you have a business plan, what they will get in return from you etcetera. So you have to be prepared to answer all these questions when you contact the companies.

Another valuable thing to keep in mind is that companies want to sponsor you and they have loads to win by getting a good reputation amongst students. This means that you have the advantage. You just have to use it, be selling and proud of your work and you will see the money starting to come in. Keep your hope up!